Morse Theory

### 2020-11-28 paper.tex
added some stuff

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin N2 
% % end N2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% % begin M2
Now, we explore Reeb graphs on manifolds of dimension 2, such that functions acting on them is a Morse function. In this case, we have a bijection between the critical points of $f$ and the nodes of $R(f)$ . We introduce the following definitions, to be able to see interesting properties of reeb graphs on orientable 2-manifolds
\begin{definition}
    Loop is a continuous function $X \to I$ where $X$ is some topological space, and $I=[0,1]$, s.t. $f(0) = f(1)$
\end{definition}
\begin{definition}
    A surface is orientable if and only if any loop on it is orientable preserving.
\end{definition}
\begin{definition}
    Loop is orientation-preserving if an only if there is a continuous choice of tangent frame along the loop such that the frame at the beggining is the same as the frame at the end
\end{definition}
For example, mobius strip is a non-orientable manifold, since if we take a normal vector accross the following loop, after one full circle it ends up in the same point but pointint to different direction.
\begin{center}
\includegraphics[width=.4\textwidth]{m1.png}
\includegraphics[width=.4\textwidth]{m2.png}
\includegraphics[width=.4\textwidth]{m3.png}
\includegraphics[width=.4\textwidth]{m4.png}
\end{center}

\textbf{Orientable Manifolds} \\
Our goal is to express number of loops in a Reeb graph by # of critical points. Let $n_i$ be the number of nodes with degree $i$. Orientable manifolds have 0 $n_2$ because every point is either minimum, maximum or saddle.\\
Therefore the number of arcs is number of connections each point has, divided by two (because we count each arc twice) is $e = (n_1+3*n_3)/2$ \\ 
number of loops is $1+e-(n_1+n_3)
% % end M2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% % begin V2
% % end V2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{9}
     \bibitem{s}
         {\sc }
         `` https://core.ac.uk/download/pdf/20670562.pdf
\end{thebibliography}

\caption{ 4 figures}
